\documentclass[12 pt]{article}

\usepackage{hyperref}

\title{Week of May 11}

\author{Jeremy Rogers \\
	\texttt{jroger44@vols.utk.edu}}

\begin{document}
	\maketitle
	
	\tableofcontents
	
	\section{Goals for the Week}
	\begin{enumerate}
		\item Install \LaTeX\ for these notes
		\item Get access to the repository and Gauley
		\item Read through all of Logan's previous notes
		\item Brush up on R by looking through the user manual
		\item Begin looking through the code on the repository
		\item Create a repository for these notes
		\item Get a Linux install working on my machine
		\item Read up on MCMC
	\end{enumerate}
	
	\section{Progress/Notes}
	
	\subsection{Install \LaTeX\ for these notes}
		\begin{enumerate}
			\item \LaTeX has been installed and tested
		\end{enumerate}
	
	\subsection{Get access to the repository and Gauley}
		 \begin{enumerate}
		 	\item With Dr. Gilchrist, I was able to get access to both repositories (the one with Logan's notes and the one containing CUBfits). I also was granted an account on Gauley and Newton.
		 \end{enumerate}
	\subsection{Read through all of Logan's previous notes} 
		\begin{enumerate}
			\item I should check out his script repository later, when I need to begin testing this. He says it's located at \url{https://github.com/ozway/cubmisc}
			\item After reading through all the notes, it appears that his code is close to completion. There are a few things that he mentioned wanting to do, and I'm not sure if he got around to those.
			\item He mentions moving some of the code to C from R, but he feels that it would be more work than it is worth.
			\item He also mentions debugging the genome creation process by using a genome that is totally dominated by mutation bias, and see if the genome is correctly created across all phi values.
			\item He also mentions changing some divisions to subtractions using logarithm rules, since that would be quicker.
			
			\item Just some terminology that I need to remember:
			\begin{enumerate}
				\item CBU -- codon usage bias
				\item $ \eta $ -- cost-benefit ratio of protein synthesis
				\item $ \phi $ -- protein synthesis rate
				\item $ N_e $ -- population size
				\item ROC -- ribosome overhead costs
				\item NSE -- nonsense error
				\item ORFs -- Open Reading Frames
				\item $ q $ -- proportional decline in fitness per ATP wasted per unit time
				\item $ \Delta M $ -- mutation bias
				\item $ E(\phi) $ -- expected protein synthesis rate, should be 1 if time units are defined correctly
				
			\end{enumerate} 
		\end{enumerate}
		
		\subsection{Read the R Manual}
		\begin{enumerate}
			\item Read the first 3 chapters
		\end{enumerate}
		
		\subsection{Read through the code on the repository}
			\begin{enumerate}
				\item I have begun to read through the main staples of the code (namely \texttt{my.cubappr.r} and \texttt{roc.appr.r}). This is a lot of code, in a language that I've only used in passing, so it could take a while to figure this out. 
			\end{enumerate}

		
		\subsection{Create a repository for these notes}
			\begin{enumerate}
				\item Repository has been created at \url{https://github.com/jeremyrogers/EEB}
			\end{enumerate}
			
		\subsection{Get a Linux Install working on my machine}
			\begin{enumerate}
				\item This is a low priority, but I'd still like to get it done by the end of the week. According to the documentation on \texttt{CUBfits}, some of the parallel stuff might bug out on Windows.
			\end{enumerate}
			
		\subsection{Read up on MCMC}
			\begin{enumerate}
				\item Thanks to Stack Exchange's math section, I found a really nice explanation on MCMC found here: \url{http://stats.stackexchange.com/questions/165/how-would-you-explain-markov-chain-monte-carlo-mcmc-to-a-layperson}.
				\item Once I got the basics down from that link, I was able to parse through the rather technical Wikipedia page on the subject, and now I feel like I have a good grasp on this.
			\end{enumerate}
\end{document}