\documentclass[12 pt]{article}

\usepackage{hyperref}
\usepackage{pdfpages}
\title{June 2015 Work Log}

\author{Jeremy Rogers \\
	\texttt{jroger44@vols.utk.edu}}

\date{June, 2015}
\begin{document}
	\maketitle
	\tableofcontents
	
	\section{Goals for the Month}
	\begin{enumerate}
		\item Gain ownership of Logan's github repository
		\item Finish running the NSE first order approximation model on all test genomes
		\item Profile the test genomes
		\item Read and understand the Murray et al. paper on doubly intractable MCMC.
		\item Get access to Preston's repository, and begin looking through the code.
		\item Clean up my log repository
	\end{enumerate}
	\section{Progress/Notes}
	\subsection{Gain ownership of the cubmisc github repository}
	\begin{enumerate}
		\item In order to gain ownership of a github repository, the current owner has to initiate the process. So I'll need to get in contact with Logan.
	\end{enumerate}
	
	\subsection{Finish running the NSE first order approximation}
	\begin{enumerate}
	\item This is in progress. I've run the REU13 yeast, Preston's Yeast, Brewers' Yeast, and Logan's yeast. Now I need to run it on the other included genomes.
	\end{enumerate}
	
	\subsection{Profile the test genomes}
	\begin{enumerate}
		\item This is also in progress, although it may take a while to get done, since I'll have to run things numerous times.
	\end{enumerate}
	
	\subsection{Read and understand the DIMCMC paper}
	\begin{enumerate}
		\item I have read over the paper a couple of times, but it's a pretty heavy paper, and it might take me a while to digest it fully.
	\end{enumerate}
	
	\subsection{Get access to Preston's repository}
	\begin{enumerate}
		\item Dr. Gilchrist has informed me that he will get me access soon.
	\end{enumerate}
	
	\subsection{Clean up my log repository}
	\begin{enumerate}
		\item My repository has been cleaned significantly, thanks to some \LaTeX\ scripts that I wrote. Now, I have separate repositories for logs, source files, and graphs. The logs directory only contains \texttt{.pdf}s, and the source directory only contains \texttt{.tex} files. All auxillary files are now stored locally on my machine so that they don't clutter up the repository anymore. 
	\end{enumerate}
\end{document}